Insurance choice, decision assistance, and insurer steering

### 2021-06-23 finals/ashecon/ashecon-202106.Rmd
update slides
update ashecon slides

2. Size of the market introduces decision problems on a massive scale

@@

- What's new here?
  - Role of decision assistance in health
  - Commissions and steering

@@

@@

- Flat commission, from <span>&#36;</span>0 to <span>&#36;</span>264
- Percentage commission, from 1% to 5% of annual premium

.pull-right[
**Sources of variation**

- Insurer
- New enrollee versus renewal
- Network type (e.g., HMO vs PPO)

>>>>

2. Size of the market introduces decision problems on a large scale

@@

- What's new here?
  - Role of decision assistance in health
  - Public and private decision assistance in the same market
  - Commissions and steering

@@

---
# What is "decision assistance"?

- Public decision assistance in the form of "navigators"
- Private brokers and agents (majority are brokers)

@@
